Adopting agile in the large: motivations, success factors and challenges

### 2013-01-25 tex/article.tex
Conclusions, sorting out todo

\begin{abstract}        % give a summary of your paper
The abstract should summarize the contents of the paper
using at least 70 and at most 150 words. It will be set in 9-point
font size and be inset 1.0 cm from the right and left margins.
There will be two blank lines before and after the Abstract.
%                         please supply keywords within your abstract
\keywords {agile, transformation, large scale, adopting agile}
\end{abstract}

@@

The goal of this research is to explore how and why large organizations adopt
agile methods. Studies on large scale agile transformations have been published,
but no extensive and summarizing research is available on the subject. In this
research we will give an overview of reported case studies on adopting agile
methods in large organizations. We will further discuss the motivations for
adopting agile methods, the characteristics of agile transformations, and
factors relating to success or challenge in the transformation process. Our
research is focused on the process of organizational change. We leave out topics
related to comparing the initial and transformed states of organisations, such
as measuring the performance of organizations before and after the
transformation.

This paper is organized as follows. The next section gives an overview of large
scale agile development. Section \ref{sec:method} presents the literature review
method used for conducting the research. The findings of the review are
discussed in section \ref{sec:results}, and section \ref{sec:conclusion}
gives proposals for future research.

@@

The selection process of the primary studies is summarized in Figure
\ref{fig:selection_process}. The database search yielded 1603 matches which were
filtered down to 31 selected primary studies. One study was not available, which
reduced the final number of primary studies to 30.
The 30 primary sources were selected by three criteria: study type, size of
organization, and use of agile methods in software development. Firstly, only
case studies and experience reports on agile software development were included
in this study. Papers discussing agile methods or organizational transformation
on as a general topic were left out. Secondly, the size of the organization
described in the included primary studies was to be large enough to show the
challenges of large scale agile development \citegen{Lindvall2004}. Further,
only studies discussing agile software development were included, leaving out
for instance studies on agile management.

@@

% \begin{table}
%     \begin{tabular}{ p{0.36\textwidth}@{ \hskip 0.2cm } l }
%         \toprule
%         Transformation mentioned in \newline text (Y/N) &
%         Large scale mentioned in text (Y/N) \\
%         Is empirical case study (Y/N) &
%         Is industry experience report (Y/N) \\
%         Has listing of practices (Y/N) &
%         Used research method (Y/N) \\
%         Relevance to this review (1-5) & \\
%         Objective of research (or publication) &
%         Research method \\
%         Author bias &
%         Validity threats \\
%         Organization size &
%         Time of transformation \\
%         Initial state of organization &
%         Why was the change initiated \\
%         How was the change conducted &
%         What is agility? / Which agile paractices are used? \\
%         Findings / lessons learned &
%         Good practices validated or suggested by study \\
%         Reported challenges &
%         Satisfaction after transformation \\
%         Effect on organization &
%         Measurements as results (quantitative or other) \\
%         Other notes &
%         Notable references \\
%         \bottomrule
%     \end{tabular}
%     \caption{The fields of the data extraction form. Fields with a (Y/N) label
%     were answered as yes or no. The field with a (1-5) label was answered by a
%     grade from 1 to 5. All other fields were answered by free form text.}
%     \label{table:dataform}
% \end{table}

%\subsection{Data sources and search strategy}
%
%\subsection{Final selection}
%
%\subsection{Data extraction and synthesis}

@@

The most commonly reported methods are listed in Table \ref{table:methods}, of
which Scrum was the most popular single method. An important observation is that
tailoring of methods was very common. The use of tailoring can be considered
relating particularly to large scale, as the core of agile methods give very
little advice on interfacing with various units present in a large organization.

@@

A particular challenge for adopting agile was misunderstanding how agile should
be applied. Some symptoms of this were talking agile but still working the old
way, and managers making commitments without hearing development teams.
As expected, many studies reported that development teams had problems
interfacing with other organizational functions, such as management and
marketing.

@@

        \raggedright\rule{0pt}{0.4cm}Effect of agile outside of development  &
            Conflicts with business (e.g. planning) [S6, S11, S21] \newline
            Making non-development functions agile (testing, maintenance, etc.) [S2, S4, S13]\newline
            Conflicts with other functions (marketing, HR, etc.) \newline[S6, S10, S11, S13] \\

@@

% ---------------------------------------------------------------------
\section{Future research}
\label{sec:conclusion}

Our results show that a body of research on large scale agile transformations
has emerged. We aim to continue research on this topic by conducting a
systematic literature review. Beyond descriptive reports on agile
transformations we found very little studies with quantitative comparison of
organizations before and after the transformations.

* -- The papers are mostly experience reports with no research method.

* -- Some papers were of low quality, but they were included in order to give a
view of the topic that is broader and inclined towards practice.

-- Effect of organizational change is hard (or maybe impossible?) to measure
(kuulemma Marjo ja Kristian tietävät asiasta).

\subsection{TODO}

eg. --> e.g.

Abstract: miksi on tärkeätä tutkia tätä?
-- Mitkä on pääasialliset löydökset?

Missä sanotaan mikä on "large"

Search kuva on selitetty myös tekstissä.

Inclusion: viewpoint on the organizational transformation [from plan-driven, tms.]

Used methods: interfacing with various units present in a large organization
--> Developmentin koordinointi

"Coaching and community" --> selitä myös coaching

Success factor: Stepwise adoption (piloting)

Conclusions:

--> Päätä siihen että "kiinnostavaa materiaalia löytyy" vaikka ei eka oletettu
--> Olemme päättäneet toteuttaa laajemman ja systemaattisen tutkimuksen aiheesta

>>>>

\begin{abstract}        % give a summary of your paper
Abstract: miksi on tärkeätä tutkia tätä?
-- Mitkä on pääasialliset löydökset?
The abstract should summarize the contents of the paper
using at least 70 and at most 150 words. It will be set in 9-point
font size and be inset 1.0 cm from the right and left margins.
There will be two blank lines before and after the Abstract.
%                         please supply keywords within your abstract
\keywords {agile, transformation, large scale, adopting agile}
\end{abstract}

@@

The goal of this research is to explore how and why large organizations adopt
agile methods. Studies on large scale agile transformations have been published,
but no extensive or summarizing research is available on the subject. In this
research we will give an overview of reported case studies on adopting agile
methods in large organizations. We will further discuss the motivations for
adopting agile methods, the characteristics of agile transformations, and
factors relating to success or challenge in the transformation process. Our
research is focused on the process of organizational change. We leave out topics
related to comparing the initial and transformed states of organisations, such
as measuring the performance of organizations before and after the
transformation.

This paper is organized as follows. The next section gives an overview of large
scale agile development. Section \ref{sec:method} presents the literature review
method used for conducting this research. The findings of the review are
discussed in section \ref{sec:results}, and section \ref{sec:conclusion}
presents limitations and proposals for future research.

@@

The selection process of the primary studies is summarized in Figure
\ref{fig:selection_process}. The database search yielded 1603 matches which were
filtered down to 31 selected primary studies. One study was not available, which
reduced the final number of primary studies to 30.
The 30 primary sources were selected by four criteria: study type, size of
organization, use of agile methods in software development, and a transformation
viewpoint. Firstly, only case studies and experience reports on agile software
development were included in this study. Papers discussing agile methods or
organizational transformation on as a general topic were left out. Secondly, the
size of the organization described in the included primary studies was to be
large enough to show the challenges of large scale agile development
\citegen{Lindvall2004}. Further, only studies discussing agile software
development were included, leaving out for instance studies on agile management.
Finally, the included studies had to provide a viewpoint on the adoption of
agile methods.

@@

@@

The most commonly reported methods are listed in Table \ref{table:methods}, of
which Scrum was the most popular single method. An important observation is that
tailoring of methods was very common. The use of tailoring can be considered
relating particularly to large scale, as the core of agile methods give very
little advice on interfacing with other units present in a large organization.
The agile team must interface with units such as other development teams,
management, and marketing.

@@

A particular challenge for adopting agile was misunderstanding how agile should
be applied. Some symptoms of this were talking agile but still working the old
way, and managers making commitments without hearing development teams.
As expected, many studies reported that teams had problems interfacing with
other organizational units, such as management and marketing.

@@

        \raggedright\rule{0pt}{0.4cm}Effect of agile outside of development  &
            Conflicts with business (e.g. planning) [S6, S11, S21] \newline
            Making non-development functions agile (testing, maintenance, etc.) [S2, S4, S13]\newline
            Conflicts with other units (marketing, HR, etc.) \newline[S6, S10, S11, S13] \\

@@

% ---------------------------------------------------------------------
\section{Limitations and future research}
\label{sec:conclusion}

The papers included in this study were mostly experience reports with no
research method. Some papers were of low quality, but they were included as our
aim was to give a view of the topic that is broader and inclined towards practice.

Differing from our initial beliefs, this research shows that a body of studies
on large scale agile transformations has emerged. We aim to continue our
research on this topic by conducting a systematic literature review. Beyond
descriptive reports on agile transformations we found very little studies with
quantitative comparison of organizations' performance before and after the
transformations.

% \subsection{TODO}

% Vielä:
% Missä sanotaan mikä on "large"
% Success factor: Stepwise adoption (piloting)

% Pitäs olla done:
% Search kuva on selitetty myös tekstissä.
% Inclusion: viewpoint on the organizational transformation [from plan-driven, tms.]
% Used methods: interfacing with various units present in a large organization
%    --> Developmentin koordinointi
% "Coaching and community" --> selitä myös coaching
